---
title: "Domenech_Analysis"
author: "Charlie Wilson"
date: "June 2021"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

Setup and packages

```{r echo = T, results = 'hide'}

#Additional packages:
library(ggplot2) 
library(ggpubr)
library(tidyr) 
library(dplyr) 
library(lubridate) 
library(svDialogs)
library(RcppRoll)

```

Function for plot DFs

```{r echo = T, results = 'hide'}
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  
    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

Setup and count and order data
Then extract it if needed
Skip to next chunk if already saved

```{r echo = T, results = 'hide'}

monkey <- dlgInput("Enter monkey", Sys.info()["user"])$res

# Where are the data?
##For Charlie Macbook
path <- file.path("/Users/charliewilson/Dropbox/Reversible Cognition/Domenech_Analysis/",monkey); #Where are the data? You need to change this for your data location
save.path <- file.path("/Users/charliewilson/Dropbox/Reversible Cognition/Domenech_Analysis"); #Path to save your data frame. Try not to put it in with the raw data

#List and organise the data
Session.list <- dir(path = path, pattern = "*.txt"); #List the files in the date
Dates <- data.frame(Session.list); #Extract dates from filenames

colnames(Dates) <- c("fid"); #rename File ID column
Dates <- Dates %>% separate(fid, c("Monkey", "Date","_","Time","Ext"),sep=cumsum(c(2,6,1,4,4))); #Split the filename into separate sections
Dates$Date <- dmy(Dates$Date); #Put Date column into date format
Dates$fid <- Session.list; 
Dates <- arrange(Dates, Date); #Put Dates into date order

Nsession <- length(Dates$Date); # How many sessions?

Data <- data.frame(); #Initialise big data frame

if(Nsession >0){ #Sanity check
  
    for(isession in 1:Nsession){ #Loop on each session  
      
      fid <- Dates$fid[isession]; #Extract filename from Dates
      print(fid) #Show filename
      event.raw <- read.csv(file=paste(path,"/",fid, sep= ""),sep= "", dec =",",  header = FALSE, fill=TRUE, colClasses=c(NA, NA,"NULL")); #Load data from .txt file using space as separator
      colnames(event.raw) <- c("time","event"); #Name columns
      event.raw$session <- isession; #Record session number
      
      # Now some basic analysis
      event.raw$trial <- cumsum(event.raw$event == 100); #Trial number
      
      # Which stimulus was used in the trial
      event.raw <- event.raw %>%
        group_by(trial) %>%   #Apply this trial by trial (rather than line by line)
        dplyr:: mutate(Stim = nth(event,4)) %>%  #In every trial take teh nth entry in the Event column
        ungroup();  #Put it back with the new column
      
      # Which TS
      event.raw <- event.raw %>%
        group_by(trial) %>%
        dplyr:: mutate(TS = nth(event,2)) %>%
        ungroup();
      
      # This is the end of intiial analysis of a single day
      
      #Put this session (event.raw) into Data which will contain all of the sessions
      Data <- rbind(Data,event.raw);
      
     rm(event.raw)
        
    }
  }

#Save
save(file = paste(save.path,"/Data_Domenech_",monkey,".Rdata",sep = ""),Data, Dates) # Save monkey specific data frame

``` 

 If you don't need to run all of the above because you have already done it, you can load the data like this:
 
```{r echo = T, results = 'hide'}

monkey <- dlgInput("Enter monkey", Sys.info()["user"])$res

# Where are the data?
save.path <- file.path("/Users/charliewilson/Dropbox/Reversible Cognition/Domenech_Analysis"); #Path to save your data frame. Try not to put it in with the raw data

load(file = paste(save.path,"/Data_Domenech_",monkey,".Rdata",sep = ""))
```


What is in each session?
 
  
```{r}
 

# Need to count the 150-153 and then look at traps as a % of this. That sets us the number of trials with an outcome

#How many traps?
Sess.data <- Data %>%
        group_by(session) %>%   #Apply this session by session
        filter(event==152) %>%   #Noisy good answer
        count(event)  #Count the instances
Sess.data2 <- Data %>%
        group_by(session) %>%   #Apply this session by session
        filter(event==153) %>%   #Noisy bad answer
        count(event)  #Count the instances
Sess.data3 <- Data %>%
        group_by(session) %>%   #Apply this session by session
        filter(event==65) %>%   #Rewards
        count(event)  #Count the instances
Sess.dat <- merge(Sess.data, Sess.data2, by="session") %>%
              merge(Sess.data3, by="session") # Combine the DFs and make sure it is done on the basis of "session"

colnames(Sess.dat) <- c("session","xx","Noiseg","yy","Noiseb","zz","Rew"); #Rename columns
Sess.dat <- subset(Sess.dat, select= -c(xx,yy,zz)); #remove superfluous columns
remove(Sess.data, Sess.data2,Sess.data3); #remove superfluous DFs

ggplot(Sess.dat, aes(x=session)) + #What data to plot
    geom_point(aes(y=Noiseg),color='red') + #Add a specific plot and colour it
    geom_point(aes(y=Noiseb),color='blue') +
    geom_point(aes(y=Rew),color='green') 

```

Let's build a trial by trial matrix to help the trial analysis, and populate it with teh necessary information on each trial and TS

```{r}

# First some summary statistics from the whole trial
Data <- Data %>%
  dplyr::group_by(session,trial) %>%
  dplyr::mutate(GNorm = sum(event == 150), BNorm = sum(event == 151),GTrap = sum(event == 152), BTrap = sum(event == 153), Rew = sum(event == 65)) %>%
  dplyr::ungroup() 

# And use that to extract if the response was correct or not
Data <- Data %>%
  dplyr::group_by(session,trial) %>%
  dplyr::mutate(COR = max(GNorm | GTrap), INC = max(BNorm | BTrap)) %>%
  dplyr::ungroup() 

# Extract response
Data <- Data %>%
  dplyr::group_by(session,trial) %>%
  dplyr::mutate(Resp = 
                  case_when(
                    sum(event == 61)>0 ~ 1,
                    sum(event == 62)>0 ~ 2,
                    sum(event == 63)>0 ~ 3)) %>%
  dplyr::ungroup() 

# Now extract the first line of each trial
rm ('Trials')
Trials <- Data %>%
  dplyr::group_by(session, trial) %>%
  slice(1)
Trials <- subset(Trials, COR>0 | INC>0) # Just trials with an outcome

# Extract the previous trial info for Stim and Rew
Trials <- Trials %>%
  dplyr::group_by(session) %>%
  dplyr::mutate(PrevSt=lag(Stim), PrevOut=lag(COR) ) %>%
  dplyr::ungroup() 

# How many rewards in the last 3 trials?
Trials <- Trials %>%
  dplyr::group_by(session) %>%
  dplyr::mutate(roll_sum = roll_sum(Rew, 4, align = "right", fill = NA)) %>%
  dplyr::ungroup() 
   
# We want a new DF with the outcomes around each trap
TrapI <- which(Trials$GTrap == 1 | Trials$BTrap == 1)

# Count trials since and to the Gtraps
Trials$GTrapCyc = cumsum(Trials$GTrap)
Trials <- Trials %>%
  group_by(GTrapCyc) %>% 
  dplyr::mutate(GTrapC = row_number()-1,GTrapCback = row_number() - (n()+1))

# Subset down to trials just around Traps and set t around Traps
rm ('Traps', 'TrapSE')
Traps <- subset(Trials, GTrapC <=2 | GTrapCback == -1)
Traps$t <-Traps$GTrapC
Traps$t[Traps$t>2] <- -1

# Is the response the same as the Trap?
Traps <- Traps %>%
  group_by(GTrapCyc) %>% 
  dplyr::mutate(TrapR = dplyr::first(Resp), SameRT = as.integer(TrapR==Resp)) 

# Is the stimulus the same as the Trap?
Traps <- Traps %>%
  group_by(GTrapCyc) %>% 
  dplyr::mutate(TrapS = dplyr::first(Stim), SameST = as.integer(TrapS==Stim))

TrapSSame <- subset(Traps, SameST == 1)
TrapSDif <- subset(Traps, SameST == 0)
```

Use this to produce a monkey version of the figures from PD's AI manuscript

```{r}
# summarySE provides the standard deviation, standard error of the mean, and a (default 95%) confidence interval
# We need the summary for the different t values -1 to 2
# But for t=2 only we need to split on the basis of PrevOut 
# The following is an ugly way of achieving this...
SS1 <- summarySE(TrapSSame, measurevar="SameRT", groupvars=c("t","PrevOut"))
SS1 <- subset(SS1, t==2 & !is.na(PrevOut),select=-PrevOut)
SS2 <- summarySE(TrapSSame, measurevar="SameRT", groupvars=c("t"))
SS2 <- subset(SS2, t<2 & t!=0)
SumSame <- rbind(SS2,SS1)

# Also for the Different stimulus...
SD1 <- summarySE(TrapSDif, measurevar="SameRT", groupvars=c("t","PrevOut"))
SD1 <- subset(SD1, t==2 & !is.na(PrevOut),select=-PrevOut)
SD2 <- summarySE(TrapSDif, measurevar="SameRT", groupvars=c("t"))
SD2 <- subset(SD2, t<2)
SumDif <- rbind(SD2,SD1)

# Reproduce figs 2a,b from the Domenech Manuscript
xxx <- c("t1-","t1+")

ggplot(SumSame, aes(x=t,y=SameRT)) + #What data to plot
    geom_point(size=3,color='red',fill='white')+
    geom_text(aes(label=ifelse(t>1,xxx,'')),hjust=2,vjust=-1) +
    geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    geom_rect(aes(xmin=-0.1, xmax=0.1, ymin=0, ymax=1), color="grey", alpha=0.1) +
    ggtitle("Same Stimulus as 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same respons as 'Neg' Trap") +
    xlab("Trials since 'Neg' Trap")
   
ggplot(SumDif, aes(x=t,y=SameRT)) + #What data to plot
    geom_point(size=3,color='blue',fill='white')+
    geom_text(aes(label=ifelse(t>1,xxx,'')),hjust=2,vjust=-1) +
    geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    geom_rect(aes(xmin=-0.1, xmax=0.1, ymin=0, ymax=1), color="grey", alpha=0.1) +
    ggtitle("Different Stimulus from 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same respons as 'Neg' Trap") +
    xlab("Trials since 'Neg' Trap")
  


# Reproduce figs 2c,d from the Domenech Manuscript

t1same <- subset(TrapSSame,t==1)
Sumt1same <- summarySE(t1same, measurevar="SameRT", groupvars=c("roll_sum"))
t1dif <- subset(TrapSDif,t==1)
Sumt1dif <- summarySE(t1dif, measurevar="SameRT", groupvars=c("roll_sum"))

ggplot(Sumt1same, aes(x=roll_sum,y=SameRT)) + #What data to plot
  geom_point()+
  geom_line(color='red')+
  geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    ggtitle("Same Stimulus as 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same response on t1 as 'Neg' Trap") +
    xlab("# Rewards in 3 trials before 'Neg' Trap")

ggplot(Sumt1dif, aes(x=roll_sum,y=SameRT)) + #What data to plot
  geom_point()+
  geom_line(color='blue') +
  geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    ggtitle("Different Stimulus from 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same response on t1 as 'Neg' Trap") +
    xlab("# Rewards in 3 trials before 'Neg' Trap")
```

Other more general plots    

```{r}

# Counter in each TS
Trials <- Trials %>%
  group_by(session, TS) %>% 
  dplyr::mutate(TScount = row_number(), TSperc = mean(COR))
#Summarise % correct
TSsum <- summarySE(Trials, measurevar="COR", groupvars=c("TScount"))
#Plot % correct through TS
ggplot(TSsum, aes(x=TScount, y=COR)) +
  geom_point()+
  geom_line(color='blue') +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 

#How well are the TSs solved?
TSs <- Trials %>%
  dplyr::group_by(session, TS) %>%
  slice(1)

ggplot(TSs, aes(x=TSperc)) +
  geom_histogram()

#Look at only the good TSs
GoodTS <- subset(Trials, TSperc>0.75)
GoodTSsum <- summarySE(GoodTS, measurevar="COR", groupvars=c("TScount"))
ggplot(GoodTSsum, aes(x=TScount, y=COR)) +
  geom_point()+
  geom_line(color='green') +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 

#Look at only the bad TSs
BadTS <- subset(Trials, TSperc<0.75)
BadTSsum <- summarySE(BadTS, measurevar="COR", groupvars=c("TScount"))
ggplot(BadTSsum, aes(x=TScount, y=COR)) +
  geom_point()+
  geom_line(color='red') +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 


```




 
 