---
title: "Domenech_Analysis_Both"
author: "Charlie Wilson"
date: "Sept 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

This is a new script for Sept 2021 to treat both Dali and Pippa data at the same time. 

Data are loaded from pre-prepared data files, see teh silenced chunks for loading of new data or parameters. 


```{r echo = FALSE, results = 'hide', warning = FALSE, message = FALSE}

#Setup and packages

#Additional packages:
library(ggplot2) 
library(ggpubr)
library(tidyr) 
#library(plyr) 
library(dplyr) 
library(lubridate) 
library(svDialogs)
library(RcppRoll)

```


```{r echo = FALSE, results = 'hide'}

# summarySE Function for plot DFs


## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence 
## interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE, conf.interval=.95) {
    library(doBy)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # Collapse the data
    formula <- as.formula(paste(measurevar, paste(groupvars, collapse=" + "), sep=" ~ "))
    datac <- summaryBy(formula, data=data, FUN=c(length2,mean,sd), na.rm=na.rm)

    # Rename columns
    names(datac)[ names(datac) == paste(measurevar, ".mean",    sep="") ] <- measurevar
    names(datac)[ names(datac) == paste(measurevar, ".sd",      sep="") ] <- "sd"
    names(datac)[ names(datac) == paste(measurevar, ".length2", sep="") ] <- "N"
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
}
```



```{r eval = FALSE, results = 'hide'}

# Setup and count and order data
# Then extract it if needed
# Skip to next chunk if already saved

monkey <- dlgInput("Enter monkey", Sys.info()["user"])$res

# Where are the data?
##For Charlie Macbook
path <- file.path("/Users/charliewilson/Dropbox/Reversible Cognition/Domenech_Analysis/",monkey); #Where are the data? You need to change this for your data location
save.path <- file.path("/Users/charliewilson/Dropbox/Reversible Cognition/Domenech_Analysis"); #Path to save your data frame. Try not to put it in with the raw data

#List and organise the data
Session.list <- dir(path = path, pattern = "*.txt"); #List the files in the date
Dates <- data.frame(Session.list); #Extract dates from filenames

colnames(Dates) <- c("fid"); #rename File ID column
Dates <- Dates %>% separate(fid, c("Monkey", "Date","_","Time","Ext"),sep=cumsum(c(2,6,1,4,4))); #Split the filename into separate sections
Dates$Date <- dmy(Dates$Date); #Put Date column into date format
Dates$fid <- Session.list; 
Dates <- arrange(Dates, Date); #Put Dates into date order

Nsession <- length(Dates$Date); # How many sessions?

Data <- data.frame(); #Initialise big data frame

if(Nsession >0){ #Sanity check
  
    for(isession in 1:Nsession){ #Loop on each session  
      
      fid <- Dates$fid[isession]; #Extract filename from Dates
      print(fid) #Show filename
      event.raw <- read.csv(file=paste(path,"/",fid, sep= ""),sep= "", dec =",",  header = FALSE, fill=TRUE, colClasses=c(NA, NA,"NULL")); #Load data from .txt file using space as separator
      colnames(event.raw) <- c("time","event"); #Name columns
      event.raw$session <- isession; #Record session number
      
      # Now some basic analysis
      event.raw$trial <- cumsum(event.raw$event == 100); #Trial number
      
      # Which stimulus was used in the trial
      event.raw <- event.raw %>%
        group_by(trial) %>%   #Apply this trial by trial (rather than line by line)
        dplyr:: mutate(Stim = nth(event,4)) %>%  #In every trial take teh nth entry in the Event column
        ungroup();  #Put it back with the new column
      
      # Which TS
      event.raw <- event.raw %>%
        group_by(trial) %>%
        dplyr:: mutate(TS = nth(event,2)) %>%
        ungroup();
      
      # This is the end of intiial analysis of a single day
      
      #Put this session (event.raw) into Data which will contain all of the sessions
      Data <- rbind(Data,event.raw);
      
     rm(event.raw)
        
    }
  }

#Save
save(file = paste(save.path,"/Data_Domenech_",monkey,".Rdata",sep = ""),Data, Dates) # Save monkey specific data frame

``` 

 First we load the data as it is currently saved and merge the databases
 
```{r echo = TRUE, results = 'hide'}

# Where are the data?
save.path <- file.path("/Users/charliewilson/Dropbox/Brain Lyon/Reversible Cognition/Domenech_Analysis"); #Path to save your data frame. Try not to put it in with the raw data

load(file = paste(save.path,"/Data_Domenech_Pippa.Rdata",sep = ""))
DataP<- Data %>%
  mutate(monkey = "P")
rm ('Data')
load(file = paste(save.path,"/Data_Domenech_Dali.Rdata",sep = ""))
DataD<- Data %>%
  mutate(monkey = "D")
rm ('Data')
Data <- rbind (DataP, DataD)
rm ('DataP', 'DataD')

```


What is in each session?
 
  
```{r echo = FALSE}
 

# Need to count the 150-153 and then look at traps as a % of this. That sets us the number of trials with an outcome

#How many traps?
Sess.data <- Data %>%
        group_by(session, monkey) %>%   #Apply this session by session
        filter(event==152) %>%   #Noisy good answer
        count(event)  #Count the instances
Sess.data2 <- Data %>%
        group_by(session, monkey) %>%   #Apply this session by session
        filter(event==153) %>%   #Noisy bad answer
        count(event)  #Count the instances
Sess.data3 <- Data %>%
        group_by(session, monkey) %>%   #Apply this session by session
        filter(event==65) %>%   #Rewards
        count(event)  #Count the instances

# Combine the DFs and make sure it is done on the basis of "session" and "monkey"
# Note that this removes completely any sessions where there is a zero count of one of the items
# Current case session 91 for P is removed...
Sess.dat <- merge(Sess.data, Sess.data2, by=c("session","monkey")) %>%
              merge(Sess.data3, by=c("session","monkey")) 

colnames(Sess.dat) <- c("session","monkey","xx","Noiseg","yy","Noiseb","zz","Rew"); #Rename columns
Sess.dat <- subset(Sess.dat, select= -c(xx,yy,zz)); #remove superfluous columns
remove(Sess.data, Sess.data2,Sess.data3); #remove superfluous DFs

Sess.dat <- pivot_longer(Sess.dat, -c(session, monkey), values_to = "Count", names_to = "Outcome")

ggplot(Sess.dat, aes(x=session, y=Count, color=Outcome)) + #What data to plot
    geom_point(aes(shape = monkey, color = Outcome))  #Add a specific plot and colour it
    

```

Let's build a trial by trial matrix to help the trial analysis, and populate it with the necessary information on each trial and TS

```{r}

# First some summary statistics from the whole trial
Data <- Data %>%
  dplyr::group_by(session,trial,monkey) %>%
  dplyr::mutate(GNorm = sum(event == 150), BNorm = sum(event == 151),GTrap = sum(event == 152), BTrap = sum(event == 153), Rew = sum(event == 65)) %>%
  dplyr::ungroup() 

# And use that to extract if the response was correct or not
Data <- Data %>%
  dplyr::group_by(session,trial,monkey) %>%
  dplyr::mutate(COR = max(GNorm | GTrap), INC = max(BNorm | BTrap)) %>%
  dplyr::ungroup() 

# Extract response
Data <- Data %>%
  dplyr::group_by(session,trial,monkey) %>%
  dplyr::mutate(Resp = 
                  case_when(
                    sum(event == 61)>0 ~ 1,
                    sum(event == 62)>0 ~ 2,
                    sum(event == 63)>0 ~ 3)) %>%
  dplyr::ungroup() 

# Now extract the first line of each trial
#rm ('Trials')
Trials <- Data %>%
  dplyr::group_by(session, trial,monkey) %>%
  slice(1)
Trials <- subset(Trials, COR>0 | INC>0) # Just trials with an outcome

# Extract the previous trial info for Stim and Rew
Trials <- Trials %>%
  dplyr::group_by(session, monkey) %>%
  dplyr::mutate(PrevSt=lag(Stim), PrevOut=lag(COR) ) %>%
  dplyr::ungroup() 

# How many rewards in the last 3 trials?
Trials <- Trials %>%
  dplyr::group_by(session,monkey) %>%
  dplyr::mutate(roll_sum = roll_sum(Rew, 4, align = "right", fill = NA)) %>%
  dplyr::ungroup() 
   
# We want a new DF with the outcomes around each trap
TrapI <- which(Trials$GTrap == 1 | Trials$BTrap == 1)

# Count trials since and to the Gtraps
# First track cycles of GTraps
Trials <- Trials %>%
  dplyr:: group_by(session,monkey) %>% 
  dplyr:: mutate(GTrapCyc = cumsum(GTrap)) %>%
  dplyr:: ungroup() 
# Then count forward and backward
Trials <- Trials %>%
  dplyr::group_by(GTrapCyc, session, monkey) %>% 
  dplyr::mutate(GTrapC = row_number()-1,GTrapCback = row_number() - (n()+1))

# Subset down to trials just around Traps and set t around Traps
#rm ('Traps', 'TrapSE')
Traps <- subset(Trials, GTrapC <=2 | GTrapCback == -1)
Traps$t <-Traps$GTrapC
Traps$t[Traps$t>2] <- -1

# Is the response the same as the Trap?
Traps <- Traps %>%
  group_by(GTrapCyc, session, monkey) %>% 
  dplyr::mutate(TrapR = dplyr::first(Resp), SameRT = as.integer(TrapR==Resp)) 

# Is the stimulus the same as the Trap?
Traps <- Traps %>%
  group_by(GTrapCyc, session, monkey) %>% 
  dplyr::mutate(TrapS = dplyr::first(Stim), SameST = as.integer(TrapS==Stim))

TrapSSame <- subset(Traps, SameST == 1)
TrapSDif <- subset(Traps, SameST == 0)
```

Use this to produce a monkey version of the figures from PD's AI manuscript

```{r warning = FALSE}
# summarySE provides the standard deviation, standard error of the mean, and a (default 95%) confidence interval
# We need the summary for the different t values -1 to 2
# But for t=2 only we need to split on the basis of PrevOut 
# The following is an ugly way of achieving this...
SS1 <- summarySE(TrapSSame, measurevar="SameRT", groupvars=c("t","PrevOut","monkey"))
SS1 <- subset(SS1, t==2 & !is.na(PrevOut),select=-PrevOut)
SS2 <- summarySE(TrapSSame, measurevar="SameRT", groupvars=c("t","monkey"))
SS2 <- subset(SS2, t<2 & t!=0)
SumSame <- rbind(SS2,SS1)

# Also for the Different stimulus...
SD1 <- summarySE(TrapSDif, measurevar="SameRT", groupvars=c("t","PrevOut","monkey"))
SD1 <- subset(SD1, t==2 & !is.na(PrevOut),select=-PrevOut)
SD2 <- summarySE(TrapSDif, measurevar="SameRT", groupvars=c("t","monkey"))
SD2 <- subset(SD2, t<2)
SumDif <- rbind(SD2,SD1)

# Reproduce figs 2a,b from the Domenech Manuscript
xxx <- c("t1-","t1-","t1+","t1+")

ggplot(SumSame, aes(x=t,y=SameRT)) + #What data to plot
    geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
    geom_text(aes(label=ifelse(t>1,xxx,'')),hjust=2,vjust=-1) +
    geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    geom_rect(aes(xmin=-0.1, xmax=0.1, ymin=0, ymax=1), color="grey", alpha=0.1) +
    ggtitle("Same Stimulus as 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same respons as 'Neg' Trap") +
    xlab("Trials since 'Neg' Trap")
   
ggplot(SumDif, aes(x=t,y=SameRT)) + #What data to plot
    geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
    geom_text(aes(label=ifelse(t>1,xxx,'')),hjust=2,vjust=-1) +
    geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    geom_rect(aes(xmin=-0.1, xmax=0.1, ymin=0, ymax=1), color="grey", alpha=0.1) +
    ggtitle("Different Stimulus from 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same respons as 'Neg' Trap") +
    xlab("Trials since 'Neg' Trap")
  

# Reproduce figs 2c,d from the Domenech Manuscript

# Summarise rolling sum of same resp
Sumt1same <- summarySE(subset(TrapSSame,t==1), measurevar="SameRT", groupvars=c("roll_sum","monkey"))
Sumt1dif <- summarySE(subset(TrapSDif,t==1), measurevar="SameRT", groupvars=c("roll_sum","monkey"))

ggplot(Sumt1same, aes(x=roll_sum,y=SameRT)) + #What data to plot
  geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
  geom_line(aes(colour=monkey))+
  geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    ggtitle("Same Stimulus as 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same response on t1 as 'Neg' Trap") +
    xlab("# Rewards in 3 trials before 'Neg' Trap")

ggplot(Sumt1dif, aes(x=roll_sum,y=SameRT)) + #What data to plot
  geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
  geom_line(aes(colour=monkey)) +
  geom_errorbar(aes(ymin=SameRT-se, ymax=SameRT+se), width=.1) +
    ylim(0,1) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    ggtitle("Different Stimulus from 'Negative' Trap on t0") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("Proportion repetition same response on t1 as 'Neg' Trap") +
    xlab("# Rewards in 3 trials before 'Neg' Trap")
```
The monkeys in the most recent dataset look very much like the "good learner" humans in the PD manuscript, without the AI lesion
This was unexpected for PD, who assumed from the Faraut et al paper that the Trap Reactivity of the monkeys shown therein was suggestive that they are doing a full reset on each Trap
I am unconvinced that this was the case (their recovery was rapid), but in any case something might well have changed between the current dataset and the start of doing this Switch Task
To test this we will need to compare the two datasets
But first we want to look quickly at how the monkeys are learning in this dataset, and the reproduce the same figs as the Faraut et al study. 
Notably until now we have been looking at selection of same response after only GTraps (good resp, -ve FB). In Faraut we were more focussed on % COR

How are the monkeys learning in the TSs in this dataset?    

```{r warning = FALSE}

# Counter in each TS
Trials <- Trials %>%
  group_by(monkey, session, TS) %>% 
  dplyr::mutate(TScount = row_number(), TSperc = mean(COR))
#Summarise % correct
TSsum <- summarySE(Trials, measurevar="COR", groupvars=c("TScount","monkey"))
#Plot % correct through TS
ggplot(TSsum, aes(x=TScount, y=COR)) +
  geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
  geom_line(aes(colour=monkey)) +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 

#How well are the TSs solved? Is there a pattern over time?
TSs <- Trials %>%
  dplyr::group_by(monkey, session, TS) %>%
  slice(1)
ggplot(TSs, aes(x=TSperc, fill = monkey)) +
  geom_histogram(position="dodge")

#Over time
TSs <- TSs %>%
    dplyr::group_by(monkey) %>%
    dplyr::mutate(TSf = as.factor(row_number()))

ggplot(TSs, aes(x=TSf, y=TSperc)) +
  geom_point(aes(colour=monkey), size=1)


#Look at only the good TSs
GoodTS <- subset(Trials, TSperc>0.75)
GoodTSsum <- summarySE(GoodTS, measurevar="COR", groupvars=c("TScount","monkey"))
ggplot(GoodTSsum, aes(x=TScount, y=COR)) +
  geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
  geom_line(aes(colour=monkey)) +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 

#Look at only the bad TSs
BadTS <- subset(Trials, TSperc<0.75)
BadTSsum <- summarySE(BadTS, measurevar="COR", groupvars=c("TScount","monkey"))
ggplot(BadTSsum, aes(x=TScount, y=COR)) +
  geom_point(aes(colour=monkey), size=3,alpha = 0.5)+
  geom_line(aes(colour=monkey)) +
  geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
  geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
  xlim(0,50) 

```
So learning is ok, but probably beneath what we had before
Significant split between TS types. 
Clear and large number of TSs where the learning hit a 50% ceiling. They are probably only learning one of the stimuli

Now we want to reproduce some of the figures from Faraut et al 2016, but for the current dataset

```{r}

#Let's look at trap reactivity as %COR (Fig 4A Faraut)

#Need to consider both Trap types, so need a Trap count that does that

# Count trials since and to the Gtraps

Trials <- Trials %>%
  group_by(monkey) %>% 
  mutate (Traps = cumsum(GTrap+BTrap))
#max(Trials$Traps)
#sum(Trials$GTrap + Trials$BTrap)

Trials <- Trials %>%
  group_by(monkey, Traps) %>% 
  dplyr::mutate(TrapC = row_number()-1,TrapCback = row_number() - (n()+1))

# Subset down to trials just around Traps and set t around Traps
#rm ('Traps', 'TrapSE')
AllTraps <- subset(Trials, TrapC <=4 | TrapCback >= -4)
AllTraps <- transform(AllTraps, tt = ifelse(TrapC>4,TrapCback,TrapC))

TrapReac <- summarySE(AllTraps, measurevar="COR", groupvars=c("tt","monkey"))

ggplot(TrapReac, aes(x=tt,y=COR)) + #What data to plot
    geom_point(aes(color=monkey),size=3,alpha=0.5)+
    geom_line(aes(color=monkey)) +
    geom_errorbar(aes(ymin=COR-se, ymax=COR+se), width=.1) +
    ylim(0.3,0.7) +
    geom_hline(aes(yintercept=0.333), colour="#990000", linetype="dashed") +
    geom_rect(aes(xmin=-0.1, xmax=0.1, ymin=0.3, ymax=0.7), color="grey", alpha=0.01) +
    ggtitle("Trap Reactivity") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylab("% Correct") +
    xlab("Trials around Trap")

```
Trap reactivity is clearly less than in the paper, on comparable pre-trap performance. 



 
 